Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
Testing different plots for 2d distribution of animal movements
fit weibull for a population, with bootstrapping.

@@

>>>>

df %>% 
  ggplot(., aes(x = xloc, y = yloc)) +
  # stat_density_2d(aes(fill = ..level..), geom = "polygon", colour="white") +
  geom_bin2d() +
  # geom_hex() +
  scale_fill_continuous(type = "viridis") +
  theme_bw()

@@

# Simulation for population 1
```{r message=FALSE}
nruns <- 20

for(j in 1:individual){
  for(k in 1:nruns){
    a <- sim_seeds(m.prms = m_1[j]) %>% 
      mutate(indiv = as.factor(j),
             run = factor(paste0("r_", k), levels = paste0("r_", 1:nruns)))

    df <- rbind.data.frame(df, a) 
    summ.df <- rbind.data.frame(summ.df, b) 
}
}
```

Visualize animal movement and seed dispersal 
```{r}
df %>% 
  ggplot(., aes(x = xloc, y = yloc)) +
  facet_wrap(~indiv) +
  # stat_density_2d(aes(fill = ..level..), geom = "polygon", colour="white") +
  geom_bin2d() +
  # geom_hex() +
  # scale_fill_continuous(type = "viridis") +
  # geom_point(data = df %>% drop_na(s.id), 
  #            aes(x = xloc, y = yloc)) +
  geom_point(data = summ.df, aes(x = x, y=y), color = "red") +
  theme_bw()
```
Seed dispersal kernels
```{r}
df %>% 
  drop_na(s.id) %>% 
  ggplot(., aes(x = disp, color = indiv)) +
  geom_density() +
  scale_color_manual(values = mycols) +
  theme_bw()

Dispersion
```{r}
summ.df %>% 
  ggplot(., aes(y = dsprsn, x = indiv)) + 
  geom_boxplot()
```
```{r}
s.df <- df %>% drop_na(s.id) %>%
  group_by(indiv) %>%
  sample_n(., 50)

# s.df <- df %>% drop_na(s.id)

weib.fits <- NULL

for(i in 1:individual){
  dat <- s.df %>% 
    filter(indiv == i)
  #g <- fitdist(dat$disp, distr = "weibull", method = 'mle', lower = c(0,0))
  g <- fitdistr(dat$disp, densfun = "weibull", lower = c(0,0))
  prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
                          est.scale = as.numeric(g$estimate[2]),
                          loglik = g$loglik, indiv = i)
  weib.fits <- rbind.data.frame(weib.fits, prms.weib)
  # plot(g)
}

weib.fits
```
Bootstrapping?
```{r}
weib.boot <- NULL

for(j in 1:10){
      s.df <- df %>% drop_na(s.id) %>%
      group_by(indiv) %>%
      sample_n(., 50)

    # s.df <- df %>% drop_na(s.id)

    weib.fits <- NULL

    for(i in 1:individual){
      dat <- s.df %>% 
        filter(indiv == i)
      #g <- fitdist(dat$disp, distr = "weibull", method = 'mle', lower = c(0,0))
      g <- fitdistr(dat$disp, densfun = "weibull", lower = c(0,0))
      prms.weib <- data.frame(est.shape = as.numeric(g$estimate[1]),
                              est.scale = as.numeric(g$estimate[2]),
                              loglik = g$loglik, indiv = i)
      weib.fits <- rbind.data.frame(weib.fits, prms.weib)
      # plot(g)
    }

    weib.boot <- rbind.data.frame(weib.boot, weib.fits %>% mutate(boot = j))
}

weib.boot
```

```{r}
library(Hmisc)

weib.boot %>% 
  ggplot(., aes(x = factor(indiv), y = est.scale)) +
  geom_violin() +
  #geom_boxplot(width = 0.1) +
  stat_summary(fun.data=mean_sdl, mult=1, 
                 geom="pointrange", color="red") +
  theme_bw()
